Appendix to 'Detecting social information in a dense database of infants’ natural

### 2021-05-28 paper/preprint/paper_revised_submission_april2021_apa.Rmd
minor wording

abstract: |
           The faces and hands of caregivers and other social partners offer a rich source of social and causal information that may be critical for infants' cognitive and linguistic development. Previous work using manual annotation strategies and cross-sectional data has found systematic changes in the proportion of faces and hands in the egocentric perspective of young infants. Here, we examine the prevalence of faces and hands in a longitudinal collection of more than 1700 headcam videos collected from three children along a span of 6 to 32 months of age—the SAYCam dataset [@SAYcam]. To analyze these naturalistic infant egocentric videos, we validated the use of a modern convolutional neural network of pose detection (OpenPose) for the detection of faces and hands and then applied this model to the entire dataset. First, we found a higher proportion of hands in view than previously reported and a moderate decrease in the proportion of faces in children's view across age. Second, we found variability in the proportion of faces/hands viewed by different children in different locations (e.g., living room vs. kitchen), suggesting that individual activity contexts may shape the social information that infants experience. Third, we found evidence that children may see closer, larger views of people, hands, and faces earlier in development. These analyses provide new insight into the changes in the social information in view across the first few years of life and call for further work that examines their generalizability across populations and their relationship to learning outcomes.

@@

# Introduction
Infants are confronted by a blooming, buzzing onslaught of stimuli [@james1890principles] which they must learn to parse to make sense of the world around them. Yet they do not embark on this learning process alone: From as early as 3 months of age, young infants follow overt gaze shifts [@gredeback2008microstructure], and even newborns prefer to look at faces with direct vs. averted gaze [@Farroni2002], despite their limited acuity. As faces are likely to be an important conduit of social information that scaffolds cognitive development, psychologists have long hypothesized that faces are prevalent in the visual experience of young infants.

@@

## Detection Method
To automatically annotate the millions of frames in SAYCam, we used a pose detector, OpenPose ^[https://github.com/CMU-Perceptual-Computing-Lab/openpose]  [@Cao2018openpose; @Simon2017hand], which provided the locations of 18 body parts (ears, nose, wrists, etc.). To do so, a convolutional neural network was used for initial anatomical detection, and part affinity fields were subsequently applied for part association to produce a series of body part candidates. Once these body part candidates were matched to a single individual in the frame, they were finally assembled into a pose. Thus, while we only made use of the outputs of the face and hand detections, the entire set of pose information from an individual was used to determine the presence of a face/hand, making the process more robust to occlusion than methods optimized to detect only faces or hands. Note, however, that these face/hand detections are reliant on the detection of at least a partial pose, so some very up-close views of faces/hands may go undetected.

@@

We suspected that this was in part because children’s own hands were often in view of the camera and unconnected to a pose--a notoriously challenging detection problem [@bambach2015lending]. To assess this possibility, we obtained human annotations for the entire subsample of 9051 frames in which a hand was detected; participants (recruited via Amazon Mechanical Turk) were asked to draw bounding boxes around children’s and adult’s hands. Overall, we found that `r round(mean(hands_missed$child_hand_seg),2)*100`% of missed hand detections were of child hands. When frames with children's hands were removed from the gold set, recall did improve somewhat to `r round(hand_performance_adults[3],2)`. We also observed that children’s hands tended to appear in the lower half of the frames; heatmaps of the bounding boxes obtained from these annotations can be seen in Appendix Figure \ref{fig:handLocation}.

Finally, we examined whether the precision, recall, and F-score for hands and faces varied with age or child, and did not find substantial variation.Thus, while OpenPose was trained on photographs from the adult perspective, this model still generalized relatively well to the egocentric infant viewpoint with no fine-tuning or post-processing of the detections. As these detections were imperfect compared to human annotators, fine-tuning these models to better optimize for the infant viewpoint remains an open avenue for future work. Standard computer vision models are rarely trained on the egocentric viewpoint, and we suspect that training these models on more naturalistic data may lead to more robust, generalizable detectors.

@@

We analyzed the social information in view across the entire dataset, looking specifically at the proportions of faces and hands detected for each child.^[All analyses and preprocessed data files for this paper are available at https://tinyurl.com/detecting-social-info] Data from videos were binned according to the age of the child (in weeks). First, we saw that the proportion of faces in view showed a moderate decrease across this age range (see Figure \ref{fig:faceHandDetailed}), in keeping with prior findings [@Fausey2016]; in contrast, we did not observe an increase in the proportion of hands in view. 
These effects were quantified with two separate linear mixed-effect models (see Tables 1 & 2)^[Face/hand detections were binned across each week of filming. Participant's age was converted into months and centered for these analyses. Random slopes for the effect of age by child led to a singular fit and were removed from both analyses; see full model specification in accompanying codebase.] After visualizing the data (see Figure \ref{fig:faceHandDetailed}A), we examined whether linear vs. quadratic terms relating children's age to the proportion of faces/hands detected would provide better fits to the data, and found that this was true in both cases (see Tables 1 & 2), though linear terms also provided a significant fit for faces. Thus, these exploratory results point towards the idea that some children may experience overall more social information in view in the second year of life.

However, the most striking result from these analyses is a much overall greater proportion of hands in view than have previously been reported [@Fausey2016]. We found this to be true across all ages, in all three children, and regardless of whether we analyzed human annotations (on the 24K random subset, see dotted lines in Appendix Figure \ref{fig:goldSetSanity}) or OpenPose annotations on the entire dataset (see Figure \ref{fig:faceHandDetailed}A). This is notable especially given that OpenPose showed relatively low recall for hands, indicating that this may be an underestimate of the proportion of hands in view. In fact, analysis of the human annotations underscores revealed a much higher proportion of hands relative to faces than the automated annotations.

One reason this could be the case is the much larger field of view that was captured by the cameras used in this study: These cameras were outfitted with a fish-eye lens in an attempt to capture as much of the children’s field of view as possible, leading to a larger field of view (109 degrees horizontal x 70 degrees vertical) than in many previous studies; for example, in @Fausey2016 the FOV was 69 x 41 degrees. This larger FOV may have allowed the SAYCam cameras to capture not only the presence of a social partner’s hands interacting with objects or gestures, but also the children’s own hands, leading to more frequent hand detections.

@@

As we found that children's hands tended to occur in the lower visual field (see Figure \ref{fig:handLocation}), we thus re-analyzed the entire dataset while restricting our analysis to the center field of view, decreasing the proportion of hand detections from `r round(sum(all_vid_data$num_hands)/sum(all_vid_data$num_frames),2)*100`% to `r round(sum(all_vid_data$num_hands_center,na.rm=TRUE)/sum(all_vid_data$num_frames),2)*100`%, but only decreased face detections from `r round(sum(all_vid_data$num_faces)/sum(all_vid_data$num_frames),2)*100`% to `r round(sum(all_vid_data$num_faces_center,na.rm=TRUE)/sum(all_vid_data$num_frames),3)*100`%. 
This cropping likely removed both the majority of detections of children's own hands but also some detections of adult hands (see Figure \ref{fig:handLocation}), especially as OpenPose was biased to miss children's hands when they were in view. 
Nonetheless, within this modified field of view, we still observed more hand detections than face detections (see dashed lines in Figure \ref{fig:faceHandDetailed}B). 
We also still found a higher proportion of hands in view relative to faces when excluding any frames containing child hand's from the human annotated gold sample (see Appendix Figure \ref{fig:goldSetSanity}).

Finally, we analyzed how these two sources of social information co-occurred, finding that faces/hands were jointly present in `r sum(all_vid_data$faces_and_hands,na.rm=TRUE)/sum(all_vid_data$num_frames)*100` percent of frames (see face hand-occurrences across age in Figure \ref{fig:faceHandDetailed}C). 
To do so, we  calculated the number of frames in which infants saw faces and hands together relative to overall proportions of faces/hands that were detected for each child and age range. As shown in Figure \ref{fig:faceHandContingency}, we found that all three infants were more likely to see hands independently -- without the presence of a face -- than they were likely to see faces independently. That is, generally speaking when a face was present, a hand also tended to be present.

@@

Figure \ref{fig:DetByLocation} shows the proportion of faces vs. hands across locations. 
We found substantial variation across locations and, to some extent, across children. 
Separate chi-squared tests for each child and detection type revealed significant variability in detections by location in each case, with all $p$s $<.001$. 
For example, while both A and S saw a relatively similar proportion of faces and hands in the bedroom, the two children saw quite different amounts of faces and hands from one another in the kitchen. 
This difference is likely explained by differences in arrangement of the kitchen in the two children's households (Sullivan, personal communication), such that mealtimes in one kitchen resulted in a face-to-face orientation while it did not in the other). 
This example illustrates how specifics of the geometry of a particular context can play an outsize role in the child's access to social information during that context.

@@

In keeping with this hypothesis, we also found evidence that faces tended to be farther away from older children. 
We restricted our analysis here to faces where both eyes were detected and computed interpupillary distance as a rough metric of distance, since eyes should be closer together on average when a face is further from the camera. 
Figure \ref{fig:faceDetailed}A shows the average interpupillary distance on faces as a function of each child’s age at the time of recording. 
There is a trend from larger, closer faces (with a larger interpupillary distance) to smaller faces that were farther away (with a smaller interpupillary distance).

@@

# General Discussion
Here, we analyzed the social information in view in a dense, longitudinal dataset, applying a modern computer-vision model to quantify the hands and faces seen from each of three children's egocentric perspective from 6 to 32 months of age. 
First, we found a moderate decrease across age in the proportion of faces in view in the videos, in keeping with previous work [@Fausey2016; @Jayaraman2015]. 
This finding is particularly notable given that, in previous cross-sectional data, this effect seems to be most strongly driven by infants younger than 4 months of age [e.g., @Fausey2016; @Jayaraman2015; @Sugden2014] who see both more frequent and more persistent faces [@Jayaraman2018]. We also found this to be true when restricting our analyses to full-field faces, suggesting this effect is not driven by a concurrent shift from more full-view to partial-views of faces.

We also found an unexpectedly high proportion of hands in the view of infants, even when restricting the field-of-view to the center field-of-view to make the viewpoints comparable to those of headcams used in prior work. Why might this be the case? One idea is that these videos contain the viewpoints of children not only during structured interactions (e.g., play sessions at home or in the lab) but during everyday activities when children may be playing by themselves or simply observing the actions of caregivers and other people in their environment. During these less structured times, caregivers may move about in the vicinity of the child but not interact with them as directly---leading to views where a person and their hands are visible from a distance, but this person's face may be turned away from the infant or occluded (see examples in Figure 1). Indeed, using the same pose detector on videos from in-lab play sessions, @sanchez2018postural found the opposite trend: slightly fewer hand detections than face detections from 8-16 months of age. Work that directly examines the variability in the social information in view across more vs. less structured activity contexts could further test this idea.

A coarse analysis based on the location the videos were filmed in further highlights the variability of the social information in view during different activities, showing differences across locations and between individual children. Within a given, well-defined context---e.g., mealtime in kitchens---S saw more faces than A, and S saw more faces in the kitchen than in other locations. This variability likely stems from the fact that there are at least three ways to feed a young child: 1) sitting in front of the child, facing them as they sit in a high chair; 2) sitting behind the child, holding them as they face outward, and 3) sitting side by side. Each of these positions offer the child differing degrees of visual access to faces and hands. While the social information in view may be variable across children in different activity contexts, these analyses suggest they could be stable within a given child's day-to-day experience.

@@

Nonetheless, we believe that these advances in datasets and methodologies represent a step in the right direction. The present paper demonstrates the feasibility of using a modern computer vision model to annotate the entirety of a very large dataset (here, >40M million frames) for the presence and size of people, hands, and faces, representing orders of magnitude more data relative to human annotations in prior work. While OpenPose did not provide annotations that were as accurate as those provided by human annotators, we found relatively consistent results with prior literature, suggesting that the sheer scale and density of the annotations provided by this method may overcome some of it's limitations. In future work, the adaptation of deep neural networks for the infant egocentric view remains a promising avenue for collaboration between computer vision experts and developmental psychologists, and indeed has already yielded new insights about the learning mechanisms needed to build visual representations [@tsutsui2020computational; @zhuang2020unsupervised; @orhan2020self]. We propose that the use of novel algorithms with large-scale analysis of dense datasets -- collected with different fields of view, cameras, and from many different laboratories -- will lead to generalizable conclusions about the regularities of infant experience that scaffold learning.

# Acknowledgements
Thanks to the creators of the SAYCam dataset who made this work possible and to Alessandro Sanchez for his contributions to the codebase. This work was funded by a Jacobs Foundation Fellowship to MCF, a John Mereck Scholars award to MCF, and NSF #1714726 to BLL.

>>>>

abstract: |
           The faces and hands of caregivers and other social partners offer a rich source of social and causal information that is likely critical for infants' cognitive and linguistic development. Previous work using manual annotation strategies and cross-sectional data has found systematic changes in the proportion of faces and hands in the egocentric perspective of young infants. Here, we examine the prevalence of faces and hands in a longitudinal collection of more than 1700 headcam videos from three children ages 6 to 32 months. To analyze these naturalistic infant egocentric videos, we validated the use of a modern convolutional neural network (OpenPose) for the detection of faces and hands and then applied this model to the entire dataset. First, we found a higher proportion of hands in view than previously reported and a moderate decrease in the proportion of faces in children's view across age. Second, we found substantial variability in the proportion of faces and hands viewed by different children in different locations (e.g., living room vs. kitchen), suggesting that individual activity contexts may shape the social information that infants experience. Third, we found evidence that children may see closer, larger views of people, hands, and faces earlier in development. These analyses provide new insight into the changes in the social information in view across the first few years of life and call for further work that examines their generalizability across populations and their relationship to learning outcomes.

@@

# Introduction
Infants are confronted by a blooming, buzzing onslaught of stimuli [@james1890principles] that they must learn to parse to make sense of the world around them. Yet they do not embark on this learning process alone: From as early as 3 months of age, young infants follow overt gaze shifts [@gredeback2008microstructure], and even newborns prefer to look at faces with direct vs. averted gaze [@Farroni2002], despite their limited acuity. As faces are likely to be an important conduit of social information that scaffolds cognitive development, psychologists have long hypothesized that faces are prevalent in the visual experience of young infants.

@@

## Detection Method
To  annotate the millions of frames in SAYCam automatically, we used a pose detector, OpenPose^[https://github.com/CMU-Perceptual-Computing-Lab/openpose]  [@Cao2018openpose; @Simon2017hand]. The OpenPose system provides the locations of up to 18 body parts (ears, nose, wrists, etc.) from individual frames. OpenPose relies on a convolutional neural network for initial anatomical detection. It then uses part affinity fields for part association to produce a series of body part candidates. Once these body part candidates are matched to a single individual in the frame, they are finally assembled into a pose. While in this study we only measured face and hand presence, the entire set of pose information from an individual was used to determine the presence of a face/hand, making the process much more robust to occlusion than methods optimized to detect *only* faces or hands. Of course, these face/hand detections are nevertheless reliant on the detection of at least a partial pose, so some very up-close views of faces/hands may still go undetected.

@@

We suspected that this was in part because children’s own hands were often in view of the camera and unconnected to a pose -- a notoriously challenging detection problem [@bambach2015lending]. To assess this possibility, we obtained human annotations for the entire subsample of 9051 frames in which a hand was detected; participants (recruited via Amazon Mechanical Turk) were asked to draw bounding boxes around children’s and adult’s hands. Overall, we found that `r round(mean(hands_missed$child_hand_seg),2)*100`% of missed hand detections were of child hands. When frames with children's hands were removed from the gold set, recall did improve somewhat to `r round(hand_performance_adults[3],2)`. We also observed that children’s hands tended to appear in the lower half of the frames; heatmaps of the bounding boxes obtained from these annotations can be seen in Appendix Figure \ref{fig:handLocation}.

Finally, we examined whether the precision, recall, and F-score for hands and faces varied with age or child, and did not find substantial variation. Thus, while OpenPose was trained on photographs from the adult perspective, this model still generalized relatively well to the egocentric infant viewpoint with no fine-tuning or post-processing of the detections. As these detections were imperfect compared to human annotators, fine-tuning these models to better optimize for the infant viewpoint remains an open avenue for future work. Standard computer vision models are rarely trained on the egocentric viewpoint, and we suspect that training these models on more naturalistic data may lead to more robust, generalizable detectors.

@@

We analyzed the social information in view across the entire dataset, looking specifically at the proportions of faces and hands detected for each child.^[All analyses and preprocessed data files for this paper are available at https://tinyurl.com/detecting-social-info] Data from videos were binned according to the age of the child (in weeks). First, we saw that the proportion of faces in view showed a moderate decrease across this age range (see Figure \ref{fig:faceHandDetailed}), in keeping with prior findings [@Fausey2016]; in contrast, we did not observe an increase in the proportion of hands in view. 
These effects were quantified with two separate linear mixed-effect models (see Tables 1 & 2).^[Face/hand detections were binned across each week of filming. Participant's age was converted into months and centered for these analyses. Random slopes for the effect of age by child led to a singular fit and were removed from both analyses; see full model specification in accompanying codebase.] After visualizing the data (see Figure \ref{fig:faceHandDetailed}A), we examined whether the addition of quadratic terms relating children's age to the proportion of faces/hands detected would provide better fit to the data than linear terms alone, and found that this was true in both cases (see Tables 1 & 2), though the linear term was also significant for faces. Thus, these exploratory results point towards the idea that some children may experience overall more social information in view in the second year of life.

However, the most striking result from these analyses is a much greater overall proportion of hands in view than has previously been reported [@Fausey2016]. We found this observation to be true across all ages, in all three children, and regardless of whether we analyzed human annotations (on the 24K random subset, see dotted lines in Appendix Figure \ref{fig:goldSetSanity}) or OpenPose annotations on the entire dataset (see Figure \ref{fig:faceHandDetailed}A). This finding is notable especially given that OpenPose showed relatively low recall for hands, indicating that our measurements may in fact be an underestimate of the proportion of hands in view. In fact, analysis of the human gold standard annotations revealed a much higher proportion of hands relative to faces than the automated annotations.

One reason we could have observed more hands in view than previous studies is the much larger field of view that was captured by the cameras used in this study. These cameras were outfitted with a fish-eye lens in an attempt to capture as much of the children’s field of view as possible, leading to a larger field of view (109 degrees horizontal x 70 degrees vertical) than in many previous studies. For example, in @Fausey2016 the FOV was 69 x 41 degrees. This larger FOV may have allowed the SAYCam cameras to capture not only the presence of a social partner’s hands interacting with objects or gestures, but also the children’s own hands, leading to more frequent hand detections.

@@

As we found that children's hands tended to occur in the lower visual field (see Figure Appendix \ref{fig:handLocation}), we thus re-analyzed the entire dataset while restricting our analysis to the center field of view, decreasing the proportion of hand detections from `r round(sum(all_vid_data$num_hands)/sum(all_vid_data$num_frames),2)*100`% to `r round(sum(all_vid_data$num_hands_center,na.rm=TRUE)/sum(all_vid_data$num_frames),2)*100`%, and face detections from `r round(sum(all_vid_data$num_faces)/sum(all_vid_data$num_frames),2)*100`% to `r round(sum(all_vid_data$num_faces_center,na.rm=TRUE)/sum(all_vid_data$num_frames),3)*100`%. 
This cropping likely removed both the majority of detections of children's own hands but also some detections of adult hands (see Figure \ref{fig:handLocation}), especially as OpenPose was biased to miss children's hands when they were in view. 
Nonetheless, within this modified field of view, we still observed more hand detections than face detections (see dashed lines in Figure \ref{fig:faceHandDetailed}B). 
We also still found a higher proportion of hands in view relative to faces when excluding any frames containing child hand's from the human annotated gold sample (see Appendix Figure \ref{fig:goldSetSanity}).

Finally, we analyzed how these two sources of social information co-occurred.
To do so, we  calculated the number of frames in which infants saw faces and hands together relative to overall proportions of faces/hands that were detected for each child and age range. Faces and hands were jointly present in `r sum(all_vid_data$faces_and_hands,na.rm=TRUE)/sum(all_vid_data$num_frames)*100` percent of frames (see face hand-occurrences across age in Figure \ref{fig:faceHandDetailed}C). As shown in Figure \ref{fig:faceHandContingency}, all three infants were more likely to see hands independently -- without the presence of a face -- than they were likely to see faces independently. That is, generally speaking when a face was present, a hand also tended to be present.

@@

Figure \ref{fig:DetByLocation} shows the proportion of faces vs. hands across locations. 
We found substantial variation across locations and, to some extent, across children. 
Separate chi-squared tests for each child and detection type revealed significant variability in detections by location in each case, with all $p$s $<.001$. 
For example, while both A and S saw a relatively similar proportion of faces and hands in the bedroom, the two children saw quite different amounts of faces and hands from one another in the kitchen. 
This difference is likely explained by differences in arrangement of the kitchen in the two children's households (Sullivan, personal communication), such that mealtimes in one kitchen resulted in a face-to-face orientation while they did not in the other. 
This example illustrates how specifics of the geometry of a particular context can play an outsize role in the child's access to social information during that context.

@@

In keeping with this hypothesis, we also found evidence that faces tended to be farther away from older children. 
We restricted our analysis here to faces where both eyes were detected and computed interpupillary distance as a rough metric of distance, since eyes should be closer together on average when a face is further from the camera. 
Figure \ref{fig:faceDetailed}A shows the average interpupillary distance on faces as a function of each child’s age at the time of recording. 
There was a trend from larger, closer faces (with a larger interpupillary distance) to smaller faces that were farther away (with a smaller interpupillary distance).

@@

# General Discussion
Here, we analyzed the social information in view in a dense, longitudinal dataset, applying a modern computer-vision model to quantify the hands and faces seen from each of three children's egocentric perspective from 6 to 32 months of age.

First, we found a moderate decrease across age in the proportion of faces in view in the videos, in keeping with previous work [@Fausey2016; @Jayaraman2015]. This finding is particularly notable given that, in previous cross-sectional data, this effect seems to be most strongly driven by infants younger than 4 months of age [e.g., @Fausey2016; @Jayaraman2015; @Sugden2014] who see both more frequent and more persistent faces [@Jayaraman2018]. We also found this to be true when restricting our analyses to full-field faces, suggesting this effect is not driven by a concurrent shift from more full-view to partial-views of faces.

We also found an unexpectedly high proportion of hands in the view of infants, even when restricting the field-of-view to the center field-of-view to make the viewpoints comparable to those of headcams used in prior work. Why might this be the case? One idea is that these videos contain the viewpoints of children not only during structured interactions (e.g., play sessions at home or in the lab) but during everyday activities when children may be playing by themselves or simply observing the actions of caregivers and other people in their environment. During these less structured times, caregivers may move about in the vicinity of the child but not interact with them as directly -- leading to views where a person and their hands are visible from a distance, but this person's face may be turned away from the infant or occluded (see examples in Figure 1). Indeed, using the same pose detector on videos from in-lab play sessions, @sanchez2018postural found the opposite trend: slightly fewer hand detections than face detections from 8-16 months of age. Work that directly examines the variability in the social information in view across more vs. less structured activity contexts could further test this idea.

A coarse analysis based on the location the videos were filmed in further highlights the variability of the social information in view during different activities, showing differences across locations and between individual children. Within a given, well-defined context -- e.g., mealtime in kitchens -- S saw more faces than A, and S saw more faces in the kitchen than in other locations. This variability likely stems from the fact that there are at least three ways to feed a young child: 1) sitting in front of the child, facing them as they sit in a high chair; 2) sitting behind the child, holding them as they face outward, and 3) sitting side by side. Each of these positions offer the child differing degrees of visual access to faces and hands. While the social information in view may be variable across children in different activity contexts, these analyses suggest they could be stable within a given child's day-to-day experience.

@@

Nonetheless, we believe that these advances in datasets and methodologies represent a step in the right direction. The present paper demonstrates the feasibility of using a modern computer vision model to annotate the entirety of a very large dataset (here, >40M million frames) for the presence and size of people, hands, and faces, representing orders of magnitude more data relative to human annotations in prior work. While OpenPose did not provide annotations that were as accurate as those provided by human annotators, we found relatively consistent results with prior literature, suggesting that the sheer scale and density of the annotations provided by this method may overcome some of it's limitations.

In future work, the adaptation of deep neural networks for the infant egocentric view remains a promising avenue for collaboration between computer vision experts and developmental psychologists. Indeed, this combination has already yielded new insights about the learning mechanisms needed to build visual representations [@tsutsui2020computational; @zhuang2020unsupervised; @orhan2020self]. We propose that the use of novel algorithms with large-scale analysis of dense datasets -- collected with different fields of view, cameras, and from many different laboratories -- will lead to generalizable conclusions about the regularities of infant experience that scaffold learning.

# Acknowledgements

Thanks to the creators of the SAYCam dataset who made this work possible and to Alessandro Sanchez for his contributions to the codebase. This work was funded by a Jacobs Foundation Fellowship to MCF, a John Merck Scholars award to MCF, and NSF #1714726 to BLL.
